Real Estate

### 2022-11-13 src/real_estate.Rmd
Filtered by MSAs with pop>500,000 at the end (put 29 MSAs data in new table).

MSA_median_rent_data <- read_sheet("https://docs.google.com/spreadsheets/d/1oxNxWQRWpANbgb603ShBlw84QkyvsRaH4TzHKKVWhxw/edit#gid=0")
```

@@

>>>>

MSA_median_rent_data <- read_sheet("https://docs.google.com/spreadsheets/d/1oxNxWQRWpANbgb603ShBlw84QkyvsRaH4TzHKKVWhxw/edit#gid=0")

select_MSAs <- read_sheet("https://docs.google.com/spreadsheets/d/1lmTpSDwVANxdAg5sW87Q8l_gtig7M0EjPPJ6J5_7dwg/edit?usp=sharing")
```

@@

```{r}
#FILTER BY NEW MSA LIST
new_MSA_list <- unique(select_MSAs$cbsa)

n_MSA_realEstate_select_MSAs <- n_MSA_realEstate %>% 
  filter(cbsa %in% c(new_MSA_list))
```
